%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item[]\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\normalItem}[1]{
  \item[-]\small{
    { #1 \vspace{-2pt}}
  }
}

\newcommand{\educationSubheading}[6]{
  \vspace{-1pt}\item[]
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
      \ifx\hfuzz#5#6\hfuzz
      \else
      \textit{\small#5} & \textit{\small #6} \\
      \fi      
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item[]
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      {\small#3} & \textit{\small #4} \\      
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\projectSubheading}[3]{
  \vspace{-1pt}\item[]
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\small#1} & {\small#2}\\
  \end{tabular*}
      {\small#3}\vspace{-5pt}
}

\newcommand{\bibSubheading}[4]{
  \vspace{-1pt}\item[]
      {\small#2},
      \ifx\hfuzz#4\hfuzz
      \textbf{\small``#1,''}      
      \else
      \href{#4}{\small``#1,''}
      \fi      
      \small{#3}
    \vspace{-2pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Qiuchen Yan}} & Email : 
  {yanxx297@umn.edu}\\
  \href{http://www-users.cs.umn.edu/~yanxx297/}
  {http://www-users.cs.umn.edu/$\sim$yanxx297/}
  & Mobile : +1-651-235-4138 \\
  \href{https://github.com/yanxx297}{https://github.com/yanxx297}
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {University of Minnesota, Twin Cities}{Minneapolis, MN}
      {Ph.D. in Computer Science;  GPA: 3.60}
      {May 2014 -- 2020 (anticipated)}
      {Master of Science in Computer Science;  GPA: 3.625}
      {Sep. 2012 -- May 2014}          
    \educationSubheading
      {Shandong University of Science and Technology}{Qingdao, China}
      {Bachelor of Engineering in Computer Science;  GPA: 3.65}
      {Sep. 2008 -- July 2012}{}{}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Research Projects}
  \resumeSubHeadingListStart  	
    \projectSubheading{Fast \& Automatic Emulator Testing}{2015 -- 2018}
    {Improve the performance of PokeEMU, an automatic emulator testing tool 
    based on FuzzBALL and KemuFuzzer.}
      \resumeItemListStart
        \normalItem{Modify the automatic test case generator of PokeEMU for better performance.}                
        \normalItem{Evaluate the improved PokeEMU by testing different versions of QEMU.}        
      \resumeItemListEnd
%        
    \projectSubheading{Loop Summarization for Symbolic Execution}{2014 -- present}
    {Implement loop summarization algorithm on FuzzBALL as a countermeasure of the path explosion problem.
    This project is supported by a grant under DARPA Cyber Grand Challenge 
    program.}
      \resumeItemListStart
      	\normalItem{Implement a trace-based loop summarization algorithm on FuzzBALL, 
      	a symbolic execution engine written in OCaml. The original algorithm is described in 
        ``Automatic Partial Loop Summarization in Dynamic Test Generation''
        (ISSTA 2011) }
        % \normalItem{Build CFG dynamically.}
        \normalItem{Evaluate the loop summarization algorithm using competition
        binaries from DARPA Cyber Grand Challenge}
      \resumeItemListEnd    
% 
    \projectSubheading{Binary Based Type Inference}{2013 -- 2014}
    {Based on heuristics and debug information except variable types, 
      infer whether the variables are signed or unsigned by computing the minimum
      cut of the data flow graph between the signed region and the unsigned region.}
  \resumeSubHeadingListEnd

%
%--------PUBLICATION------------
\section{Publication}
	\resumeSubHeadingListStart
    	\bibSubheading{Fast PokeEMU: Scaling Generated Instruction Tests Using 
        Aggregation and State Chaining}
        {\textbf{Qiuchen Yan}, Stephen McCamant}
        {The 14th ACM SIGPLAN/SIGOPS International Conference on Virtual Execution Environments (VEE'18)}
        {http://www-users.cs.umn.edu/~yanxx297/vee18-fast-pokeemu.pdf}
    	\bibSubheading{Fast PokeEMU: Scaling Generated Instruction Tests Using 
      Aggregation and State Chaining}
        {\textbf{Qiuchen Yan}, Stephen McCamant}
        {Poster}
        {http://www-users.cs.umn.edu/~yanxx297/posterFastPokeEMU.pdf}     
        \bibSubheading{Conservative Signed/Unsigned Type Inference for Binaries
        using Minimum Cut}
        {\textbf{Qiuchen Yan}, Stephen McCamant}
        {Technical report}
        {https://www.cs.umn.edu/research/technical_reports/view/14-006}             
    \resumeSubHeadingListEnd         

%
%--------EXPERIENCE------------
\section{Experience}
  \resumeSubHeadingListStart
  \projectSubheading
      {Graduate Research Asistant, University of Minnesota}{2014 -- present}
      {Work with Stephen McCamant on several research projects. 
      Collaborate with Pen-Chung Yew's dynamic binary translation group on the emulator testing project.}    
    \projectSubheading
      {DARPA Cyber Grand Challenge}{2014 -- 2015}
      {In addition to the loop summarization project, contributed code for 
      FuzzBOMB group in CGC Qualification Event.}  
  \resumeSubHeadingListEnd
  
  
%
%--------PROGRAMMING SKILLS------------
\section{Skills}	
 \resumeSubHeadingListStart
 	\resumeItem{Programming Languages}
    {C/C++, Python, OCaml, X86 assembly, Javascript, PHP, SQL} 
  \resumeItem{Systems \& Tools}
    {Linux, Xed (Intel Pin), DWARF, Vine, FuzzBALL}
  \resumeItem{Version Control System}{Git}
 \resumeSubHeadingListEnd

%
%--------RELATED COURSEWORK------------
\section{Coursework}
  \resumeSubHeadingListStart
    \resumeItem
      {Introduction to Computer Security}
      {A breadth of knowledge about software security and network security}   
    \resumeItem
      {Modern Cryptography}
      {Introduction to widely used cryptography theories and algorithms}
    \resumeItem
      {Machine Learning}
      {Introduction to machine learning}      
    \resumeItem
      {Security and Privacy in Computing}
      {A seminar discussing recent papers about security, privacy and cryptography}
  \resumeSubHeadingListEnd  

%-------------------------------------------
\section{Academic Projects}
\resumeSubHeadingListStart  	
\projectSubheading{Reproduce the Lucky Thirteen attack}{2014}
{Implemented a timing side channel attack to the TLS protocol. 
Course project.}
\projectSubheading{Sybil attack study}{2014}
{Surveyed about the Sybil attack in online social network and its state-of-art defence approach
and collected data from real world sybil communities in sina weibo. 
Course project.}
\projectSubheading{Encrypted address book}{2012}
{An Android address book app that can send encrypted contact info via text message. 
Bachelor final project.}
\resumeSubHeadingListEnd

%-------------------------------------------
\section{Service}
\resumeItemListStart
\normalItem{Contributed to open source projects (FuzzBALL and PyXed.)}
\normalItem{Gave guest lectures on security related courses at the University of Minnesota.}
\resumeItemListEnd
\end{document}
